\documentclass[11pt]{article}
\sloppy
\usepackage{fullpage,palatino,amssymb,amsmath,amsfonts}
\usepackage{hyperref}

\usepackage{bbm}
\usepackage{mathpple}

\renewcommand{\ttdefault}{cmtt}
\SetMathAlphabet\mathtt{normal}{OT1}{cmtt}{m}{n}

\begin{document}

\title{CS~310, Assignment 1} 
 \author{Monica Li}
% \date{}
 \maketitle

\begin{enumerate}

\item Let $\Sigma = \{0, 1\}$ and consider the languages
  $A = \{10, 00, 0\}$ and $B = \{01, 11, 1\}$.
  \begin{enumerate}
  \item Write down all strings in $\Sigma^{*}$ that have length at
    most two. \\
    $\epsilon, 0, 1, 00, 01, 10, 11$
  \item How many strings are in $A \cdot B$?  Write down all of them.\\
  There are 8 strings in $A \cdot B$: $1001, 1011, 101, 0001, 0011, 001, 011, 01$
  \item How many strings are in $B \cdot A$?  Write down all of them. \\
  There are 8 strings in $B \cdot A$: $0110, 0100, 010, 1110, 1100, 110, 100, 10$
  \end{enumerate}
\item Let $R = (ba^{*}b + aba^{*}ba)^{*}$ and
  $S = (a^{*}ba^{*}ba^{*})^{*}$, both over $\Sigma=\{a,b\}$.
  \begin{enumerate}
  \item Give an example of a string $z$ that is both in $R$ and in $S$
    (that is, $z \in R \cap S$ ). \\
    $bb$
  \item Is it possible to find a string $x$ that is in $R$ and is not
    in $S$ (that is, $x \in R \cap \overline{S}$)?  If yes, write it
    down; if not explain briefly why. \\
    No, because $R = (ba^{*}b + aba^{*}ba)^{*} = (ba^{*}b)^{*} + (aba^{*}ba)^{*} $\\
    Both $(ba^{*}b)^{*}$ and $(aba^{*}ba)^{*} \subset S$, so $R \subset S $. Therefore $R \cap \overline{S} = \O$
  \item Is it possible to find a string $y$ that is in $S$ and is not
    in $R$ (that is, $y \in S \cap \overline{R}$)?  If yes, write it
    down; if not explain briefly why. \\
    $y = baba$ 
  \end{enumerate}
\item Show how to define the following languages over
  $\Sigma = \{0, 1\}$ using only $\varepsilon$, the alphabet symbols
  $0$ and $1$, and the operations of union, concatenation, and
  closure.

  \begin{enumerate}
  \item All strings that begin with $11$ \emph{and} end with $10$. \\
  $11(0+1)^{*}10$
  \item All strings that have both $10$ and $01$ as substrings. Note
    that the substrings can occur in either order and possibly
    overlap. \\
    $((0+1)^{*}101(0+1)^{*})+((0+1)^{*}010(0+1)^{*})+((0+1)^{*}10(0+1)^{*}01(0+1)^{*})+((0+1)^{*}01(0+1)^{*}10(0+1)^{*})$
  \end{enumerate}

\item Describe the language $L$ defined by each of the following
  equations.  Explain briefly.

  \begin{enumerate}
  \item $L = 1 + L0 + 0L$ \\
  $1$ is an element of $L$; for any $l \in L$, $l0$ and $0l$ are also in $L$; these are the only elements of $L$. So $L = \{ 0^{i}10^{j}, i \geq 0, j \geq 0 \}$
  \item $L = L + L$ \\
  $L_{0} = \O, L_1 = L_{0} + L_{0} = \O + \O = \O, ..., L_{j+1} = L_j + L_j = \O$\\
  $L = \O$
  \end{enumerate}
\end{enumerate}

\end{document}
